Does the leaf economic spectrum hold within plant functional types? A Bayesian hierarchical meta-analysis

### 2018-02-16 manuscript/index.Rmd
Add acknowledgements and author contributions
Also, count words manually. R package hugely overestimates words for
some reason.

```{r wordcount, echo = FALSE}
fnames <- c(
  introduction = "01_introduction.md",
  methods = "02_methods.Rmd",
  results = "03_results.Rmd",
  discussion = "04_discussion.md"
)
files <- here::here(
  "manuscript", 
  fnames
)
names(files) <- names(fnames)

getwc <- function(f) {
  ct <- withr::with_options(
    list(knitr.table.format = "pandoc"),
    wordcountaddin::text_stats(f)
  )
  wline <- ct[3]
  wlist <- strsplit(wline, split = "[[:space:]]+")
  as.numeric(wlist[[1]][3])
}

wc_table <- data.frame(wordcount = vapply(files, getwc, numeric(1)))
wc_total <- rbind(wc_table, sum(wc_table$wordcount))
wc_total$percent <- 100 * wc_total$wordcount / 
  sum(wc_total$wordcount[-nrow(wc_total)])
rownames(wc_total)[nrow(wc_total)] <- "total"
knitr::kable(wc_total, digits = 1)
```

>>>>

Section                   Word count          
--------                  --------------      ------------
Introduction              1060                Figures:
Materials and Methods     1603                6 (all colored)
Results                   1073
Discussion                1789                Tables:
Acknowledgements          88                  2
Total                     5613
